SeisAcoustic

### 2019-06-26 docs/latex/Acoustic_FWI/paper.tex
add multi-sources simulation in frequency domain

\tilde{p}_z^{it-1+\frac{1}{2}} = {{\bf d}_p{\bf d}_z}^T \cdot {{\bf M}_{vz}{\bf B}_{p}} \cdot \tilde{v}_z^{it-1}+  {{\bf d}_p{\bf d}_x}^T \cdot {{\bf M}_{vx}{\bf B}_{p}} \cdot \tilde{v}_x^{it-1} + \tilde{p}_z^{it+\frac{1}{2}} \\  

@@

\subsection{Born approximation}
Researchers commonly use born approximation to derive the gradient for FWI, here we show the result obtained based on matrix formulation is consistent with the gradient derived based on Born approximation.  
The first order acoustic wave equation can be expressed as
\begin{equation}
\begin{split}
 \frac{\partial v_z}{\partial t} &=  b \frac{\partial p}{\partial z}  \\
 \frac{\partial v_x}{\partial t} &=  b \frac{\partial p}{\partial x}  \\
\frac{\partial p}{\partial t} &= k \left(\frac{\partial v_z}{\partial z} + \frac{\partial v_x}{\partial x} \right) + f(t)
\end{split}
\label{eq82}
\end{equation}
We still assume the density is constant, the scatter wave field is produced by the perturbation of velocity model $v$, so the new wave field is governed by the following equations:
 \begin{equation}
 \begin{split}
\frac{\partial (v_z + \Delta v_z)}{\partial t} &=  b \frac{\partial (p + \Delta p) }{\partial z} \\
\frac{\partial (v_x + \Delta v_x)}{\partial t} &=  b \frac{\partial (p + \Delta p) }{\partial x} \\
\frac{\partial (p + \Delta p)}{\partial t} &= \rho (v+\Delta v)^2 \left( \frac{\partial (v_z + \Delta v_z)}{\partial z} + \frac{\partial( v_x +\Delta v_x)}{\partial x} \right)+ f(t)\\
\end{split}
\label{eq83}
 \end{equation}
Subtracting equation \ref{eq83} by equation \ref{eq82} and ignore the higher order terms, we get the scattered wave field equations as
\begin{equation}
\begin{split}
\frac{\partial \Delta v_z}{\partial t} &= b \frac{\partial }{\partial z} \left(\Delta p_z  + \Delta p_x \right) \\
\frac{\partial \Delta v_x}{\partial t} &=  b \frac{\partial }{\partial x} \left(\Delta p_z  + \Delta p_x \right) \\
\frac{\partial  \Delta p}{\partial t} &= k \left( \frac{\partial  \Delta v_z}{\partial z} +  \frac{\partial  \Delta v_z}{\partial z} \right) + 2\rho v \Delta v \left( \frac{\partial v_z}{\partial z} +  \frac{\partial v_z}{\partial z} \right) \\
\end{split}
\label{eq84}
\end{equation}
From the last equation of equations \ref{eq82}, we know
\begin{equation}
\frac{\partial v_z}{\partial z} +  \frac{\partial v_z}{\partial z}  = \frac{\frac{\partial p}{\partial t} - f(t)}{k}
\label{eq85}
\end{equation}
We can use this equation to replace the terms in equation \ref{eq83}, we can get
\begin{equation}
\begin{split}
\frac{\partial \Delta v_z}{\partial t} &= b \frac{\partial }{\partial z} \left(\Delta p_z  + \Delta p_x \right) \\
\frac{\partial \Delta v_x}{\partial t} &=  b \frac{\partial }{\partial x} \left(\Delta p_z  + \Delta p_x \right) \\
\frac{\partial  \Delta p}{\partial t} &= k \left( \frac{\partial  \Delta v_z}{\partial z} +  \frac{\partial  \Delta v_z}{\partial z} \right) + \frac{2\left( \frac{\partial p}{\partial t} - f(t)\right)}{v} \Delta v  \\
\end{split}
\label{eq86}
\end{equation}
We usually call the term in front of $\Delta v$ as the source-side wave filed, which is 
\begin{equation}
\frac{2\left( \frac{\partial p}{\partial t} - f(t)\right)}{v}
\label{eq87}
\end{equation}
The gradient of the velocity model is obtained by zero-lag cross-correlation between source-side wave field and the adjoint wave field.
Which is consistent with the discretized form give in equation \ref{eq81} as
\begin{equation}	
{\bf diagm} \left( \frac{2({\bf p}^{it+\frac{1}{2}} - {\bf p}^{it-\frac{1}{2}}  - dt \cdot {\bf f}^{it})}{{\bf v}} \right) 
\label{eq88}
\end{equation}
The only difference between above two equations is $dt$, which come from the discretization of equation \ref{eq84}, and equation \ref{eq88} can be obtained by multiplying equation \ref{eq85} by $dt$.

>>>>

\tilde{p}_x^{it-1+\frac{1}{2}} = {{\bf d}_p{\bf d}_z}^T \cdot {{\bf M}_{vz}{\bf B}_{p}} \cdot \tilde{v}_z^{it-1}+  {{\bf d}_p{\bf d}_x}^T \cdot {{\bf M}_{vx}{\bf B}_{p}} \cdot \tilde{v}_x^{it-1} + \tilde{p}_x^{it+\frac{1}{2}} \\  

@@

\subsection{Born approximation}
Researchers commonly use born approximation to derive the gradient for FWI, here we show the result obtained based on matrix formulation is consistent with the gradient derived based on Born approximation.  
The first order acoustic wave equation can be expressed as
\begin{equation}
\begin{split}
 \frac{\partial v_z}{\partial t} &=  b \frac{\partial p}{\partial z}  \\
 \frac{\partial v_x}{\partial t} &=  b \frac{\partial p}{\partial x}  \\
\frac{\partial p}{\partial t} &= k \left(\frac{\partial v_z}{\partial z} + \frac{\partial v_x}{\partial x} \right) + f(t)
\end{split}
\label{eq82}
\end{equation}
We still assume the density is constant, the scatter wave field is produced by the perturbation of velocity model $v$, so the new wave field is governed by the following equations:
 \begin{equation}
 \begin{split}
\frac{\partial (v_z + \Delta v_z)}{\partial t} &=  b \frac{\partial (p + \Delta p) }{\partial z} \\
\frac{\partial (v_x + \Delta v_x)}{\partial t} &=  b \frac{\partial (p + \Delta p) }{\partial x} \\
\frac{\partial (p + \Delta p)}{\partial t} &= \rho (v+\Delta v)^2 \left( \frac{\partial (v_z + \Delta v_z)}{\partial z} + \frac{\partial( v_x +\Delta v_x)}{\partial x} \right)+ f(t)\\
\end{split}
\label{eq83}
 \end{equation}
Subtracting equation \ref{eq83} by equation \ref{eq82} and ignore the higher order terms, we get the scattered wave field equations as
\begin{equation}
\begin{split}
\frac{\partial \Delta v_z}{\partial t} &= b \frac{\partial }{\partial z} \left(\Delta p_z  + \Delta p_x \right) \\
\frac{\partial \Delta v_x}{\partial t} &=  b \frac{\partial }{\partial x} \left(\Delta p_z  + \Delta p_x \right) \\
\frac{\partial  \Delta p}{\partial t} &= k \left( \frac{\partial  \Delta v_z}{\partial z} +  \frac{\partial  \Delta v_x}{\partial x} \right) + 2\rho v \Delta v \left( \frac{\partial v_z}{\partial z} +  \frac{\partial v_x}{\partial x} \right) \\
\end{split}
\label{eq84}
\end{equation}
From the last equation of equations \ref{eq82}, we know
\begin{equation}
\frac{\partial v_z}{\partial z} +  \frac{\partial v_x}{\partial x}  = \frac{\frac{\partial p}{\partial t} - f(t)}{k}
\label{eq85}
\end{equation}
We can use this equation to replace the terms in equation \ref{eq83}, we can get
\begin{equation}
\begin{split}
\frac{\partial \Delta v_z}{\partial t} &= b \frac{\partial }{\partial z} \left(\Delta p_z  + \Delta p_x \right) \\
\frac{\partial \Delta v_x}{\partial t} &=  b \frac{\partial }{\partial x} \left(\Delta p_z  + \Delta p_x \right) \\
\frac{\partial  \Delta p}{\partial t} &= k \left( \frac{\partial  \Delta v_z}{\partial z} +  \frac{\partial  \Delta v_z}{\partial z} \right) + \frac{2\left( \frac{\partial p}{\partial t} - f(t)\right)}{v} \Delta v  \\
\end{split}
\label{eq86}
\end{equation}
We usually call the term in front of $\Delta v$ as the source-side wave filed, which is 
\begin{equation}
\frac{2\left( \frac{\partial p}{\partial t} - f(t)\right)}{v}
\label{eq87}
\end{equation}
The gradient of the velocity model is obtained by zero-lag cross-correlation between source-side wave field and the adjoint wave field.
Which is consistent with the discretized form give in equation \ref{eq81} as
\begin{equation}	
{\bf diagm} \left( \frac{2({\bf p}^{it+\frac{1}{2}} - {\bf p}^{it-\frac{1}{2}}  - dt \cdot {\bf f}^{it})}{{\bf v}} \right) 
\label{eq88}
\end{equation}
The only difference between above two equations is $dt$, which come from the discretization of equation \ref{eq84}, and equation \ref{eq88} can be obtained by multiplying equation \ref{eq85} by $dt$.
